Binary companions of evolved stars in \apogee\ \DR: \\ Search method and catalog of $\sim$5,000 companions

### 2018-04-03 paper/1-catalog/twoface-catalog.tex
Links to website

From this run, 91,096 stars completed and successfully returned \nposterior\
samples using \thejoker\ alone.
The remaining 5,135 stars did not return \nposterior\ samples: 4,744 were
flagged as \emph{needs more prior samples}, 391 as \emph{needs MCMC}.
We then proceed to generate \nposterior\ samples for these two subsets using the
methodology explained above (see \sectionname~\ref{sec:samplings}).
% In the end, \todo{XX} stars have completed samplings with \nposterior\ samples,
% and, after re-running \thejoker\ with twice as many prior samples, \todo{XX}
% stars still have fewer samples that are multi-modal in period.
The full catalog of posterior samples for all \apogee\ stars in our parent
sample is available online.
\todo{Structure of table, where to download, make a webpage with some
information?}

@@

Starting from the high-$K$ sample, we select stars that have posterior period
samples that fall within a single mode.
We define a period resolution for each star $\Delta =
\left[4\,P_{\textrm{min}}^2 / (2\pi \, T) \right]$, where $P_{\textrm{min}}$ is
the minimum period sample value, and $T$ is the epoch span of the data for that
star.
We consider a sampling to be unimodal when
\begin{equation}
    P_{\textrm{max}} - P_{\textrm{min}} < \Delta \label{eq:unimodal}
\end{equation}
(see \sectionname~2 of \citealt{Price-Whelan:2017}); \nunimodal\ stars
pass this cut.
Unlike the multi-modal stars, the posterior \pdf 's for these stars can be
approximated using point-estimates and standard deviations of their respective
samplings.
We report maximum \textit{a posteriori} (MAP) sample values for the orbital
parameters, along with other computed quantities for all \nunimodal\ stars in
this high-$K$, unimodal sample.
For stars with measured primary masses, $M_1$, from other work
(\citealt{Ness:2015}), we compute the minimum companion mass, $M_{2,
\textrm{min}}$ and include both masses in this catalog.
We additionally join with the \apogee\ \DR\ \texttt{allStar} catalog and provide
all columns from this catalog for convenience.
\tablename~\ref{tbl:highK-unimodal} contains descriptions and units for all
columns in the high-$K$, unimodal sample catalog, available online.
\todo{Link to a webpage with the catalogs and info on how to use with
TwoBody/TheJoker}

@@

We have selected a catalog of nearly 5,000 stellar systems with companions by
making cuts on posterior beliefs about the amplitude of orbital radial velocity
variations for often low-epoch, sparsely sampled radial velocity data.
We provide posterior samplings over orbital parameters for all \nstars\ in the
parent sample of \apogee\ \DR\ systems used in this work, along with several
sub-catalogs with better constrained orbital information:
\begin{itemize}
    \item A catalog of \nunimodal\ systems with unimodal posterior samplings,
    and therefore uniquely determined orbits, of which 225 are newly discovered
    binary star systems.
    \item A catalog of \nbimodal\ systems with highly constrained posterior
    samplings that, in period, span two distinct period modes.
    For these systems, one or a few more radial velocity measurements would
    uniquely determine their orbits.
    90 of these systems are newly discovered binary star systems.
    \item A catalog of \nhighK\ systems with radial velocity variations
    consistent with having a companion, but which need further radial velocity
    measurements to better constrain the orbital properties.
\end{itemize}
All companion catalogs described in this work (\sectionname~\ref{sec:catalogs})
are available online at \todo{XX}.

@@

\section{Using data products...}
\label{sec:code-demo}

\todo{Brief example of how to use twobody and thejoker to visualize orbits, with
link to a tutorial notebook on github}

@@

% Notebook: HighK-multimodal
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-bimodal}
\end{center}
\caption{%
TODO
\label{fig:highK-bimodal}
}
\end{figure}

>>>>

From this run, 91,096 stars completed and successfully returned \nposterior\
samples using \thejoker\ alone.
The remaining 5,135 stars did not return \nposterior\ samples: 4,744 were
flagged as \emph{needs more prior samples}, 391 as \emph{needs MCMC}.
We then proceed to generate \nposterior\ samples for these two subsets using the
methodology explained above (see \sectionname~\ref{sec:samplings}).
% In the end, \todo{XX} stars have completed samplings with \nposterior\ samples,
% and, after re-running \thejoker\ with twice as many prior samples, \todo{XX}
% stars still have fewer samples that are multi-modal in period.
The full catalog of posterior samples for all \apogee\ stars in our parent
sample is available online.\footnote{\url{http://adrian.pw/twoface.html}}

@@

Starting from the high-$K$ sample, we select stars that have posterior period
samples that fall within a single mode.
We define a period resolution for each star $\Delta =
\left[4\,P_{\textrm{min}}^2 / (2\pi \, T) \right]$, where $P_{\textrm{min}}$ is
the minimum period sample value, and $T$ is the epoch span of the data for that
star.
We consider a sampling to be unimodal when
\begin{equation}
    P_{\textrm{max}} - P_{\textrm{min}} < \Delta \label{eq:unimodal}
\end{equation}
(see \sectionname~2 of \citealt{Price-Whelan:2017}); \nunimodal\ stars
pass this cut.
Unlike the multi-modal stars, the posterior \pdf 's for these stars can be
approximated using point-estimates and standard deviations of their respective
samplings.
We report maximum \textit{a posteriori} (MAP) sample values for the orbital
parameters, along with other computed quantities for all \nunimodal\ stars in
this high-$K$, unimodal sample.
For stars with measured primary masses, $M_1$, from other work
(\citealt{Ness:2015}), we compute the minimum companion mass, $M_{2,
\textrm{min}}$ and include both masses in this catalog.
We additionally join with the \apogee\ \DR\ \texttt{allStar} catalog and provide
all columns from this catalog for convenience.
\tablename~\ref{tbl:highK-unimodal} contains descriptions and units for all
columns in the high-$K$, unimodal sample catalog, available online.\footnote{\url{http://adrian.pw/twoface.html}}

@@

We have selected a catalog of nearly 5,000 stellar systems with companions by
making cuts on posterior beliefs about the amplitude of orbital radial velocity
variations for often low-epoch, sparsely sampled radial velocity data.
We provide posterior samplings over orbital parameters for all \nstars\ in the
parent sample of \apogee\ \DR\ systems used in this work, along with several
sub-catalogs with better constrained orbital information:
\begin{itemize}
    \item A catalog of \nunimodal\ systems with unimodal posterior samplings,
    and therefore uniquely determined orbits, of which 225 are newly discovered
    binary star systems.
    \item A catalog of \nbimodal\ systems with highly constrained posterior
    samplings that, in period, span two distinct period modes.
    For these systems, one or a few more radial velocity measurements would
    uniquely determine their orbits.
    90 of these systems are newly discovered binary star systems.
    \item A catalog of \nhighK\ systems with radial velocity variations
    consistent with having a companion, but which need further radial velocity
    measurements to better constrain the orbital properties.
\end{itemize}
All companion catalogs described in this work (\sectionname~\ref{sec:catalogs})
are available online.\footnote{\url{http://adrian.pw/twoface.html}}

@@

\section{Data products}
\label{sec:code-demo}

% \todo{Brief example of how to use twobody and thejoker to visualize orbits, with
% link to a tutorial notebook on github}

@@

% Notebook: HighK-multimodal
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-bimodal}
\end{center}
\caption{%
Randomly-selected examples of high-$K$ stars with bimodal posterior samplings.
Same as \figurename~\ref{fig:highK-unimodal}, but for bimodal posterior
samplings.
\label{fig:highK-bimodal}
}
\end{figure}
